Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-25 sections/eval.tex
Update on Overleaf.

\begin{align*}
    \finchplan(queries..., names...) \quad\quad\quad \finchquery(name, expr) \quad\quad\quad \finchreorder(expr, idxs...)\\
    \finchrelabel(expr, idxs...) \quad\quad\quad \finchmapjoin(op, exprs...) \quad\quad\quad \\
    \finchaggregate(op, expr)\quad\quad\quad \finchtable(tns, idxs...)  \quad\quad\quad\quad\quad \finchalias(name) \quad\quad\\
     expr:= \finchreorder | \finchrelabel |\finchmapjoin | \finchaggregate | \finchtable | \finchalias\quad\quad
\end{align*}

>>>>

\begin{align*}
    \finchplan(queries..., names...) \quad\quad\quad \finchquery(name, expr) \quad\quad\quad \finchreorder(expr, idxs...)\\
     \finchrelabel(expr, idxs...) \quad\quad\quad \finchreformat(expr, format) \quad\quad\quad \finchmapjoin(op, exprs...) \\
    \finchaggregate(op, expr)\quad\quad\quad\quad \finchtable(tns, idxs...)  \quad\quad\quad\quad\quad\quad \finchalias(name) \quad\quad\\
     expr:= \finchreorder | \finchrelabel | \finchreformat |\finchmapjoin | \finchaggregate | \finchtable | \finchalias \quad\quad
\end{align*}
